\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-17 NAR_DRAFT.tex
fix supp fig S1 and add smaller file size png version
trying to get figure 3 to fit in the text at a reasonable place
non-breaking spaces

\begin{equation}
  \label{eqn:computed_posterior}
  $$
  \frac{\mathrm{P}(m,\nu = \hat{f})}{1 - \mathrm{P}(m,\nu = \hat{f})} = 10^{\mathrm{TLOD} + \mathrm{logit}_{10}(\mathrm{p}(\mathrm{S}_{m,c}))},
  $$
\end{equation}
where $\mathrm{p}(\mathrm{S}_{m,c})$ is the prior probability of a substitution of type $\mathrm{S}_{m,c}$, as described in equation \ref{eqn:detailed_prior} and specified in equations \ref{eqn:post_pred} - \ref{eqn:mut_rate}.
When comparing our posterior odds to those of MuTect in this paper, we following \citet{Cibulskis2013} in assuming a prior per-base probability of mutation of $3\cdot10^{-6}$.
We compute the posterior odds for Mutect as
\begin{equation}
  \label{eqn:mutect_posterior}
  $$
  \frac{\mathrm{P}(m,\nu = \hat{f})}{1 - \mathrm{P}(m,\nu = \hat{f})} = 10^{\mathrm{TLOD} - 6},
  $$
\end{equation}
since $\mathrm{logit}_{10}(3\cdot10^{-6}) \approx -6$.

@@

\begin{figure}
  \begin{center}
  \includegraphics{figures/kl_only.pdf}
  \end{center}
  \caption{KL divergence between the estimated profile ($\boldsymbol{\pi}$) and the simulated mutation profile for \textbf{(A)} Whole exomes and \textbf{(B)} whole genomes.
  The estimated mutation profile converges quickly to the target as the number of mutations evaluated rises.}
\label{NAR-kl_fig}
\end{figure}

@@

@@

\begin{figure}[b]
  \begin{center}
  \includegraphics{figures/fig_wgs.pdf}
  \end{center}
  \caption{Model performance on 100X simulated whole genome.
  \textbf{(A)} Precision recall curves and \textbf{(B)} Reciever operating characteristic curves for 3 mutation signatures.
  Distribution of estimated true positive probabilities for true positive  variants for \textbf{(C)} the MuTect model and \textbf{(D))} the \batcave model.
  A perfectly calibrated model would generate the diagonal line.}
\label{NAR-wgs_fig}
\end{figure}

>>>>

\begin{equation}
  \label{eqn:computed_posterior}
  $$
  \frac{\mathrm{P}(m,\nu = \hat{f})}{1 - \mathrm{P}(m,\nu = \hat{f})} = 10^{\mathrm{TLOD} + \mathrm{logit}_{10}(\mathrm{p}(\mathrm{S}_{m,c}))},
  $$
\end{equation}
where $\mathrm{p}(\mathrm{S}_{m,c})$ is the prior probability of a substitution of type $\mathrm{S}_{m,c}$, as described in equation~\ref{eqn:detailed_prior} and specified in equations~\ref{eqn:post_pred}--\ref{eqn:mut_rate}.
When comparing our posterior odds to those of MuTect in this paper, we following Cibulskis et al., 2013~\citep{Cibulskis2013} in assuming a prior per-base probability of mutation of $3\cdot10^{-6}$.
We compute the posterior odds for Mutect as
\begin{equation}
  \label{eqn:mutect_posterior}
  $$
  \frac{\mathrm{P}(m,\nu = \hat{f})}{1 - \mathrm{P}(m,\nu = \hat{f})} = 10^{\mathrm{TLOD} - 6},
  $$
\end{equation}
since $\mathrm{logit}_{10}(3\cdot10^{-6}) \approx -6$.

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=.35\textwidth]{figures/kl_only.pdf}
  \end{center}
  \caption{KL divergence between the estimated profile ($\boldsymbol{\pi}$) and the simulated mutation profile for \textbf{(A)} Whole exomes and \textbf{(B)} whole genomes.
  The estimated mutation profile converges quickly to the target as the number of mutations evaluated rises.}
\label{NAR-kl_fig}
\end{figure}

@@

\begin{figure}[b]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/fig_wgs.png}
  \end{center}
  \caption{Model performance on 100X simulated whole genome.
  \textbf{(A)} Precision recall curves and \textbf{(B)} Reciever operating characteristic curves for 3 mutation signatures.
  Distribution of estimated true positive probabilities for true positive  variants for \textbf{(C)} the MuTect model and \textbf{(D))} the \batcave model.
  A perfectly calibrated model would generate the diagonal line.}
\label{NAR-wgs_fig}
\end{figure}
